---
title: "Huron-Manistee National Forests, 2023"
author: "Claire Burtrum with substantial code contributions from Myles Walimaa"
---

<font size="4"> 
**These LANDFIRE-Powered Landscape Assessments allow users to start exploring trends, landscape conversion and natural resource management options. **

</font> 


## Goals of this quick demonstration

We will use [LANDFIRE](https://landfire.gov/){target="blank"} products to:

1. Map and summarize past and present ecosystems and ecosystem conditions
2. Explore historical disturbance regimes
3. Summarize patterns of change and management opportunities


The following charts, maps, and graphs are based on current LANDFIRE products, however they are intended only as a starting point for further analysis. 


## Interacting with this web report
A few notes about using this report:

* As of May 3, 2023 there has been no QAQC.  This is a demo only.
* This platform is web-hosted so you can simply share a link with collaborators for their review.  
* Maps and charts are intended to represent general patterns, and are almost always limited to most common types (e.g., ecosystems).  You can use the "zoom" tool to take a closer look.
* All maps, input datasets and further assistance can be obtained by contacting [Randy Swaty](mailto:rswaty@tnc.org).


## Location of this assessment
Huron-Manistee administrative boundary, retrieved from [FSGeodata Clearinghouse](https://data.fs.usda.gov/geodata/edw/datasets.php?dsetCategory=boundaries){target="blank"}.


<br>

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}

library(foreign)
library(sf)
library(terra)
library(tidyverse)
library(raster)


```


```{r read shapefile, message=FALSE, warning=FALSE, include=FALSE}
#  read shape
shp <- st_read("data/") %>% 
  st_transform(crs = 5070) %>%
  st_union() %>%
  st_sf() %>%
  st_make_valid()


plot(shp)
```

```{r locator map, message=FALSE, warning=FALSE, echo=FALSE}
library(tmap)

# toggle tmap mode to interactive viewing
tmap_mode("view")

# create a quick interactive map
quickmap <- qtm(shp, 
                borders = "darkgreen", 
                fill = NULL, 
                check.and.fix = TRUE, 
                basemaps = 'https://server.arcgisonline.com/ArcGIS/rest/services/World_Topo_Map/MapServer/tile/{z}/{y}/{x}',
                title = 'Huron-Manistee National Forest',)

quickmap



```

## How to use this web report

* All maps, input datasets and further assistance can be obtained by contacting the author and USFS GIS Analyst, [Claire Burtrum](mailto:claireburtrum@gmail.com) or Nature Conservancy LANDFIRE ecologist [Randy Swaty](mailto:rswaty@tnc.org){target="blank"}.
* Review is ongoing.
* To share this web app, simply share the hyperlink.
* Toggle between dark and light display of this site in the upper right corner of the page.
* Learn more about LANDFIRE and The Nature Conservancy [here](about.qmd){target="blank}. 
